### 2022-10-30 doc/src/IOMMU.tex
Tighten behavior of MSI PTE MRIF mode for unsupported memory accesses
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

Memory accesses by I/O devices to addresses within a page
covered by an MRIF-mode PTE are handled by the IOMMU
instead of being passed through to the memory system.
For a read access, the IOMMU returns zero as the read value.
A write access is either interpreted as an MSI, resulting
in an update of the destination MRIF, or is discarded.

@@

If an incoming write access is for a data size other
than 32~bits or the address is not \mbox{32-bit}-aligned,
then the write is accepted by the IOMMU but discarded.
Otherwise, if the write is to guest physical address~$A$ and its
\mbox{32-bit} data is~$D$ when interpreted in the byte order indicated
by bit~2 of $A$, then the write is processed as follows:
If either $A$\z{[}11:3\z{]} or $D$\z{[}31:11\z{]} is not zero, or if
bit~2 of $A$ is one and big-endian MSIs are not supported, then the
incoming write is accepted but discarded.
Else, the original incoming write is recognized
as an MSI and is replaced by this sequence:
\begin{enumerate}

>>>>

Memory accesses by I/O devices to addresses within a page
covered by an MRIF-mode PTE are handled by the IOMMU
instead of being passed through to the memory system.
If a memory access, read or write, is not for 32~bits of data,
or if the access address is not aligned to a 4-byte boundary
(including accesses that straddle the page boundary),
the access should be aborted as unsupported.
For a naturally aligned 32-bit read, the IOMMU should preferably
return zero as the read value but may alternatively abort the access.
A naturally aligned 32-bit write is either interpreted as an MSI, resulting
in an update of the destination MRIF, or is discarded.

@@

If a naturally aligned 32-bit write is to guest physical address~$A$
within a page covered by an MRIF-mode PTE, and if the write
data is~$D$ when interpreted in the byte order indicated
by bit~2 of $A$, then the write is processed as follows:
If either $A$\z{[}11:3\z{]} or $D$\z{[}31:11\z{]} is not zero, or if
bit~2 of $A$ is one and big-endian MSIs are not supported, then the
incoming write is accepted but discarded.
Else, the original incoming write is recognized
as an MSI and is replaced by this sequence:
\begin{enumerate}
